% Chapter 7

\chapter{Conclusions and Recommendations} % Write in your own chapter title
\label{Chapter7}
%\lhead{Chapter 7. \emph{Conclusions and Recommendations}} % Write in your own chapter title to set the page header
Conclusions and recommendations have already presented in Chapter \ref{Chapter4} for individual assets under investigation. This section is hence only to provide a high level conclusions and recommendations.
\section{Conclusions}
\begin{itemize}
\item Pumps have been operated in non-optimal control approach that might lead to higher failure probability of total system failure in a long run;
\item Daily data on operation and power consumption is poorly recorded in non-relational table structure that is of little use for data analysis, especially when considering the huge amount of data recorded over time. This data shall be considered a very important part of management as it shall be used for energy audit and investigation on reliability of pumps and the system;
\item No real time measurement of production and power consumption per pump. This leads to the impossibility of calculating the reliability of pump over time;
\item No systematic inspection/testing strategy;
\item Piping supports suffer significant deterioration and wear out;
\item Existing FDAS system is not working;
\item No lighting and grounding protection system in place.
\end{itemize}

\section{Recommendations}
\begin{itemize}
\item Establishment of control philosophy to optimally operate pumps in a manner to protect pumps from being failed;
\item Establishment of a good asset management practice (see recommendation in the Appendix);
\item Establishment of a benchmark value for monitoring energy efficiency;
\item Hiring an asset management expert/specialist to help the IAM to design a good platform to record data concerning daily production and power consumption via web-based system (This does not need to involve a consulting company. Hiring a specialist to work with the IAM will eventually save cost for Maynilad in a long run);
\item Establishment of an optimal inspection/testing regime for all assets. This testing regime shall be developed using the concept of optimality based on a solid mathematical modeling approach and best practices learnt from the industry (e.g. case based reasoning methodology);
\item Redesign the FDAS system, lighting and grounding system. This shall be an immediate action to be executed prior to next raining season.

%\item 
\end{itemize}



